A pipeline to analyse time-course gene expression data

### 2019-09-24 scripts/manuscript.Rmd
fix error in Rmd code

# Let's keep only the list of genes that have a label.
labels = unlist(labels[!is.na(labels)])
```

@@

```{r fig.height=6, fig.width=6}
cluster2Score = names(labels[labels==2])
#order them by their score
cluster2Score=cluster2Score[order(scores_and_labels$scores[cluster2Score,2], decreasing = TRUE)]
dataToPlot=rbind(data[cluster2Score[1:4], ],"Centroid"=kmeans_clusters$centroids[2,])
plot_splines_data(dataToPlot, moanin_model,
    colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
    mar=c(1.5,2.5,2,0.1))
```

@@

The source code for this workflow can be found at
[https://github.com/NelleV/2019timecourse-rnaseq-pipeline](https://github.com/NelleV/2019timecourse-rnaseq-pipeline).
Archived source code at the time of publication can be foud at [XXX](XXX).

>>>>

# Let's keep only the list of genes that have a label.
labels = unlist(labels[!is.na(labels)])
cluster2Score = names(labels[labels==2])
```

@@

```{r fig.height=6, fig.width=6}
#order them by their score
cluster2Score=cluster2Score[order(scores_and_labels$scores[cluster2Score,2], decreasing = TRUE)]
dataToPlot=rbind(data[cluster2Score[1:4], ],"Centroid"=kmeans_clusters$centroids[2,])
plot_splines_data(dataToPlot, moanin_model,
    colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
    mar=c(1.5,2.5,2,0.1))
```

@@

The source code for this workflow can be found at
[https://github.com/NelleV/2019timecourse-rnaseq-pipeline](https://github.com/NelleV/2019timecourse-rnaseq-pipeline).
Archived source code at the time of publication can be found at [XXX](XXX).
